The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2017-02-04 reviews/2017-02-response-to-reviewers.tex

\makeatletter
\renewcommand{\subsection}{\clearpage\@startsection{section}{1}{0mm}
{\baselineskip}{\baselineskip\medskip\hrule\medskip}{\raggedright\Large\bf~\textcolor{MidnightBlue}}}
\makeatother

\newcommand{\critique}[1]{\begin{quote}#1\end{quote}}
\newcommand{\answer}[1]{{\setlength{\parindent}{0pt}\par\color{blue} #1}}
\newcommand{\tb}[1]{\textcolor{blue}{#1}}
\newcommand{\answerok}[1]{{\setlength{\parindent}{0pt}\par\color{MidnightBlue} #1}}
\newcommand{\unclear}[1]{\textcolor{red}{\sf [C: #1]}}

\vspace{3cm}
Dear Todd Gureckis,

\bigskip
Thank you for the vivifying report and reviewer comments you sent us for our revision to CS15-80.

\medskip
Attached is the final version of the manuscript, updated with the suggestions from reviewer \#3 as well as a few minor stylistic and bibliographic fixes for production.

### 2017-02-04 brainscopycut.tex
formatting: fix section titles to look as requested for submission
formatting: better subsubsection spacing
formatting: add figure placement indications for manuscript format
formatting: clean up source tex from irrelevant comments
formatting: fix all references
affiliation

% General document style ------------------------------------------------------------------
\documentclass[man]{apa6}
%\documentclass[man]{apa6}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumerate}

@@

%\acmVolume{VV}
%\acmNumber{N}
%\acmYear{YYYY}
%\acmMonth{Month}
%\acmArticleNum{XXX}
%\acmdoi{10.1145/XXXXXXX.YYYYYYY}

%\markboth{S. Lerique and C. Roth}{How do we copy and paste? The semantic drift of quotations in blogspace}

@@

% Formatting bibliography
%\usepackage{natbib}
\usepackage[natbibapa,nodoi]{apacite}
%\setcitestyle{authoryear,round,semicolon}

% Mathematics and Code
\usepackage{amsmath}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage[group-separator={,}]{siunitx}
%\usepackage{stmaryrd}
\usepackage{xfrac}
\usepackage{mathtools}
%\newcommand{\defeq}{\overset{\underset{\mathrm{def}}{}}{=}}

% Strikethrough (with the \sout comment)
\usepackage[normalem]{ulem}

@@

% Have graphics
\graphicspath{{images/}}
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}

@@

% To make comments, corrections, notes
\newcommand{\tb}[1]{\textcolor{blue}{#1}}
\newcommand{\tbn}[1]{\tb{\sout{#1}}}
%\newcommand{\tg}[1]{\textcolor{MidnightBlue}{#1}}
\newcommand{\tg}[1]{{#1}}
\newcommand{\newtext}[1]{\tg{#1}}
%\newenvironment{new}{\par\color{MidnightBlue}}{\par}
\newenvironment{new}{\par}{\par}
\newcommand{\add}[1]{\tb{ADD: #1}}
\newcommand{\ra}[1]{$\rightarrow$#1}
\newcommand{\replace}[2]{\sout{#1} \tb{#2}}
\newcommand{\rk}[1]{\tb{{\footnotesize {\bf[\emph{#1}]}}}}
\newcommand{\marginnote}[1]{\marginpar{{\parbox{1.\linewidth}{\hrulefill\\\tb{\scriptsize \sf #1}}}}}
\newcommand{\cam}[1]{\tb{\small{[{\bf C:} }#1{]}}}
\newcommand{\seb}[1]{\tb{\small{[{\bf S:} #1{]}}}}
\newcommand{\todo}[1]{\tb{#1}}
\definecolor{lightblue}{rgb}{.85,.85,1}
\definecolor{lightgreen}{rgb}{.85,1,.85}

@@

@@

\title{The semantic drift of quotations in blogspace: a case study in short-term cultural evolution}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}
\abstract{
\newtext{We present an empirical case study which connects psycholinguistics with the field of cultural evolution, in order to test for the existence of cultural attractors in the evolution of quotations.
Such attractors have been proposed as a useful concept for understanding cultural evolution in relation with individual cognition, but their existence has been hard to test.
We focus on the transformation of quotations when they are copied from blog to blog or media website:
by coding words with a number of well-studied lexical features, we show that the way words are substituted in quotations is consistent (1) with the hypothesis of cultural attractors, and (2) with known effects of the word features.
In particular, words known to be harder to recall in lists have a higher tendency to be substituted, and words easier to recall are produced instead.
Our results support the hypothesis that cultural attractors can result from the combination of individual cognitive biases in the interpretation and reproduction of representations.}
}
\authornote{\emph{Keywords:} word recall; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; psycholinguistics.\\\emph{Corresponding author:} Sébastien Lerique, CAMS, EHESS, 190 av. de France, F-75013 Paris. Email: sebastien.lerique@normalesup.org.}
\keywords{\newtext{word recall}; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

@@

@@

>>>>

% General document style ------------------------------------------------------------------
%\documentclass[jou]{apa6}
\documentclass[man]{apa6}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumerate}

@@

@@

% Formatting bibliography
\usepackage[natbibapa]{apacite}

% Mathematics and Code
\usepackage{amsmath}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage[group-separator={,}]{siunitx}
\usepackage{xfrac}
\usepackage{mathtools}

@@

% Have graphics
\graphicspath{{images/}}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

% To make comments, corrections, notes
\newcommand{\tb}[1]{\textcolor{blue}{#1}}
\newcommand{\tbn}[1]{\tb{\sout{#1}}}
\newcommand{\tg}[1]{{#1}}
\newcommand{\newtext}[1]{\tg{#1}}
\newenvironment{new}{\par}{\par}
\newcommand{\add}[1]{\tb{ADD: #1}}
\newcommand{\ra}[1]{$\rightarrow$#1}
\newcommand{\replace}[2]{\sout{#1} \tb{#2}}
\newcommand{\rk}[1]{\tb{{\footnotesize {\bf[\emph{#1}]}}}}
\newcommand{\marginnote}[1]{\marginpar{{\parbox{1.\linewidth}{\hrulefill\\\tb{\scriptsize \sf #1}}}}}
\newcommand{\cam}[1]{\tb{\small{[{\bf C:} }#1{]}}}
\newcommand{\seb}[1]{\tb{\small{[{\bf S:} #1{]}}}}
\newcommand{\todo}[1]{\tb{#1}}
\definecolor{lightblue}{rgb}{.85,.85,1}
\definecolor{lightgreen}{rgb}{.85,1,.85}

@@

% Fix subsubsection to look as requested for submission
\renewcommand{\typesectitle}[1]{#1\hfill\\ \vskip0.2\baselineskip \hskip-1em}

% Add figure placement indications in apamode "man"
\newcommand{\indicatemanfigure}[1]{
\ifapamode{%man
  \begin{center}
    -------------------------- Insert Figure \ref{#1} about here --------------------------
  \end{center}
}{%jou
}{%doc
}}

@@

\title{The semantic drift of quotations in blogspace: a case study in short-term cultural evolution}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and\\Centre Marc Bloch Berlin e.V., UMIFRE 14 CNRS/MAEDI, Friedrichstr. 191, D-10117 Berlin}{Sciences Po, médialab, Paris, France\\and\\Centre Marc Bloch Berlin e.V., UMIFRE 14 CNRS/MAEDI, Friedrichstr. 191, D-10117 Berlin}
\abstract{
\newtext{We present an empirical case study which connects psycholinguistics with the field of cultural evolution, in order to test for the existence of cultural attractors in the evolution of quotations.
Such attractors have been proposed as a useful concept for understanding cultural evolution in relation with individual cognition, but their existence has been hard to test.
We focus on the transformation of quotations when they are copied from blog to blog or media website:
by coding words with a number of well-studied lexical features, we show that the way words are substituted in quotations is consistent (1) with the hypothesis of cultural attractors, and (2) with known effects of the word features.
In particular, words known to be harder to recall in lists have a higher tendency to be substituted, and words easier to recall are produced instead.
Our results support the hypothesis that cultural attractors can result from the combination of individual cognitive biases in the interpretation and reproduction of representations.}
}
\authornote{\emph{Keywords:} word recall; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; psycholinguistics.\\\emph{Corresponding author:} Sébastien Lerique, CAMS, EHESS, 190 av. de France, F-75013 Paris. Email: sebastien.lerique@normalesup.org.}

@@

% Force section numbering
\setcounter{secnumdepth}{3}

@@

% Remove section numbering for references
\setcounter{secnumdepth}{0}
